Multi-domain, multilingual translation with latent multi-task group dropout

### 2021-11-15 2022/acl/acl_latex.tex
relecture complete

\subsection{System design and configuration}
\subsubsection{Multidomain translation systems}
Our systems for the multidomain experiments are designed as follows:
\begin{itemize}
\item Transformer: The embedding dimension for both encoder and decoder is set as 512, and the feedforward dimension is 2048; the multi-head attention mechanism contains 8 heads;
\item Adapter-based Transformer: The intermediate feedforward dimension is set to 2048;% as in \citet{Pham21revisiting}.
\item \system{LaMGD} Transformer:\fyTodo{Explain acronym} There is no change in the architecture. We group the 512 nodes in each layer into 16 groups of 32 consecutive nodes. For each domain, only 12 out of the 16 groups are selected. The number of parameters of the variational distributions is $k \times L \times n_d$, which is negligible when compared to the size of the Transformer model;
\end{itemize}

We set the dropout probability as 0.1. We train the multi-domain Transformer model for 20k iterations with a batch size of 12k tokens. We train \system{LaMGD} Tranformer for 300k iterations with a batch size of 12k tokens: these extra iterations are justified by the need for the \system{LaMGD} Tranformer to learn both the sub-networks and the parameters of the underlying Transformer. Finally, we plug domain Adapters to the multidomain Transformer model and finetune them for 25k iterations using the same batch size as the baseline.

@@

We set the dropout probability as 0.3. We train the multilingual Transformer model in 40~K iterations with a batch size of 9600 tokens on 16 GPUs as in \citet{Gong21adaptive}. We train \system{LaMGD} Tranformer for 50k iterations with the same batch size. Finally, we finetune the language-specific Adapters for 5k iterations.

@@

\subsection{Datasets}
\subsubsection{Multidomain translation}
We use the same data as in the recent work of \citet{Pham21revisiting} on multidomain translation.\fyTodo{Add public to the data link} We describe the datasets for multidomain translation experiments in Table~\ref{tab:Corpora-chap4}.
\begin{table*}[h!]
  \centering
  \begin{tabular}{|l|cccccc|} %*{4}{|r|}}
    \cline{2-7} 
    \multicolumn{1}{c|}{} & \multicolumn{1}{c}{\domain{med}} & \multicolumn{1}{c}{\domain{law}} & \multicolumn{1}{c}{\domain{bank}} & \multicolumn{1}{c}{\domain{it}} & \multicolumn{1}{c}{\domain{talk}} & \multicolumn{1}{c}{\domain{rel}} \\
    \hline 
    \# lines & 2609 (0.68) & 501 (0.13) & 190 (0.05) & 270 (0.07) & 160 (0.04) & 130 (0.03) \\
    \# \revisiondone{tokens}  &  133 / 154  &  17.1 / 19.6 &  6.3 / 7.3 &  3.6 / 4.6 &  3.6 / 4.0 &  3.2 / 3.4 \\
    \# \revisiondone{types}  & 771 / 720 & 52.7 / 63.1 & 92.3 / 94.7 & 75.8 / 91.4 & 61.5 / 73.3 & 22.4 / 10.5 \\
    \# \revisiondone{uniq} & 700 / 640 & 20.2 / 23.7 & 42.9 / 40.1 & 44.7 / 55.7 & 20.7 / 25.6 & 7.1 / 2.1 \\
    \hline
  \end{tabular}
  \caption{Corpora statistics: number of parallel lines ($\times 10^3$) and proportion in the basic domain mixture (which does not include the \domain{news} domain), number of tokens in English and French ($\times 10^6$), number of types in English and French ($\times 10^3$), number of types that only appear in a given domain ($\times 10^3$). \domain{med} is the largest domain, containing almost 70\% of the sentences, while \domain{rel} is the smallest, with only 3\% of the data.
  }
\label{tab:Corpora-chap4}
\end{table*}
\subsubsection{Multilingual translation}
We evaluate our model on both one-to-many (O2M) and many-to-one (M2O)
translation tasks borrowing the multilingual translation datasets from past studies. More precisely, we used: 
\begin{itemize}
\item TED8-Related. Following the setting of \citet{Wang20balancing}, we use a subset of translations from \citet{qi18when} between English and eight \emph{related languages}.
\item TED8-Diverse. The dataset consists of parallel sentences between English and eight \emph{diverse languages} as in \citet{Wang20balancing}.
\end{itemize}

@@

\subsection{Multidomain translation}
For these experiments, our main results are in Table ~\ref{tab:mdmt}, where we observe that the \system{LaMGD} Tranformer achieves a significant improvement (+2.78) over the generic \system{Transformer} system with zero extra parameters. Moreover, \system{LaMGD} Tranformer achieves performance that are equivalent on average to that of the \system{Adapter} sytems, which is carrefully finetuned and contains approximately 12.4M additional parameters.
\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{4cm}|*{7}{r|}} \hline
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[65m]} & 40.3 & 59.5 & 49.8 & 36.4 & 49.0 & 80.0  & 52.5\\
    \revision{\system{Adapter}}   \hfill{\footnotesize[+12.4m]}  & 39.5 & 61.0 & 53.1 & 37.5 & 49.6 & 91.0 & 55.28 \\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}  & 40.3 & 60.4 & 52.4 & 39.0 & 52.4 & 87.5 & 55.33 \\ 
    \hline
  \end{tabular}
  \caption{Multi-domain translation}
  \label{tab:mdmt}
\end{table*}
\subsubsection{Fuzzy domain separation}
\label{ssec:fuzzy}
In this experiment, we reuse an experiment proposed by \citet{Pham21revisiting} which measures the efficiency of a multi-domain NMT system exploiting the proximity between domains. The experiment uses the same data as the previous experiment. However, the domain \domain{law} is now randomly split into two pseudo domains \domain{law$_1$} and \domain{law$_2$}. If the multi-domain system made full use of the proximity between \domain{law$_1$} and \domain{law$_2$}, there should be no significant difference between the performance of the system trained with six original domains and with seven domains replacing \domain{law} by \domain{law$_1$} and \domain{law$_2$}. \citet{Pham21revisiting} showed a large gap between two training settings when using residual adapters. We report below the gap between two settings when using \system{LaMGD} Tranformer.

\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{4cm}|*{2}{r|}} \hline
    Model / Domain & \multicolumn{1}{c|}{\domain{law$_1$}} & \multicolumn{1}{c|}{\domain{law$_2$}} \\ \hline 
    \system{Adapter}   \hfill{\footnotesize[+25m]}  & -0.6 & -0.8 \\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}  & 0.0 & 0.0 \\ 
    \hline
  \end{tabular}
  \caption{Fuzzy domain separation}
  \label{tab:fuzzy}
\end{table*}

Table \ref{tab:fuzzy} demonstrates a significant loss when training with two pseudo domains \domain{law$_1$} and \domain{law$_2$} compared to training with the real domain \domain{law}. Our system does not have this loss between two situations. In Section \ref{ssec:abalation}, we show that our algorithm outputs the same sub-network for \domain{law$_1$} and \domain{law$_2$}, that allows a full transfer between two domains.

\subsection{Multilingual translation}
According to Table \ref{tab:multilingual}, \system{LaMGD} Tranformer shows a boost of 0.42, 0.33, 0.32 in average over the multilingual \system{Transformer} in O2M-related, M2O-related, M2O-diverse respectively. Significant gains are observed in \domain{bel}, \domain{glg} (both direction), \domain{hin} and \domain{bos} (O2M direction) which are very low-resourced languages in the list. However, \system{LaMGD} Tranformer lags behind multilingual \system{Transformer} and Language Adapters in O2M-diverse. 
\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{4cm}|*{9}{r|}} \hline
    O2M-related & \multicolumn{1}{c|}{\domain{aze}} & \multicolumn{1}{c|}{\domain{ bel}} & \multicolumn{1}{c|}{\domain{ces}} & \multicolumn{1}{c|}{\domain{glg}} & \multicolumn{1}{c|}{\domain{por}} & \multicolumn{1}{c|}{\domain{rus}} & \multicolumn{1}{c|}{\domain{slk}} & \multicolumn{1}{c|}{\domain{tur}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[91.6m]} & 4.8 &7.3&20.8&21.1&39.7&19.8&22.6&15.2&18.9 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]} &4.3&6.8&21.1&22&39.7&20&23&15.2&19 \\ 
    \system{LaMGD} Tranformer  \hfill{\footnotesize[+0m]}  & 5.2&\SB{9.4}&20.6&\SB{22.8}&39.6&19.6&22.4&15.0&19.33 \\ 
	\hline
    \hline
    M2O-related & \multicolumn{1}{c|}{\domain{aze}} & \multicolumn{1}{c|}{\domain{ bel}} & \multicolumn{1}{c|}{\domain{ces}} & \multicolumn{1}{c|}{\domain{glg}} & \multicolumn{1}{c|}{\domain{por}} & \multicolumn{1}{c|}{\domain{rus}} & \multicolumn{1}{c|}{\domain{slk}} & \multicolumn{1}{c|}{\domain{tur}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[67.8m]} &11.4&16.6&28.5&	27.1&43.7&24.6&30.3&25.6&25.98 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]} &10.1&15.8&28.4&26.8&43.7&24.5&30.2&25.6&25.64\\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}  &11.3&\SB{17.4}&28.6&\SB{28.7}&43.7&24.5&30.7&25.6&26.31 \\ 
    \hline
    \hline
    O2M-diverse & \multicolumn{1}{c|}{\domain{bos}} & \multicolumn{1}{c|}{\domain{mar}} & \multicolumn{1}{c|}{\domain{hin}} & \multicolumn{1}{c|}{\domain{mkd}} & \multicolumn{1}{c|}{\domain{ell}} & \multicolumn{1}{c|}{\domain{bul}} & \multicolumn{1}{c|}{\domain{fra}} & \multicolumn{1}{c|}{\domain{kor}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[96.9m]} & 10.2&4&12.7&22.2&31.8&\SB{34}&38.3&8.3&20.19 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]}  &10.2&4&\SB{13.3}&21.9&32.2&\SB{34.1}&38.5&8.3&20.31 \\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}&10.1&3.8&12.6&\SB{22.8}&31.8&33.4&38.1&8.1&20.09\\
    \hline 
    \hline
    M2O-diverse & \multicolumn{1}{c|}{\domain{bos}} & \multicolumn{1}{c|}{\domain{mar}} & \multicolumn{1}{c|}{\domain{hin}} & \multicolumn{1}{c|}{\domain{mkd}} & \multicolumn{1}{c|}{\domain{ell}} & \multicolumn{1}{c|}{\domain{bul}} & \multicolumn{1}{c|}{\domain{fra}} & \multicolumn{1}{c|}{\domain{kor}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[70.4m]} &22.4&9.7&20.5&31.8&37.5&38.7&39.8&19&27.43 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]}  &22.5&9.4&20&30.6&37.2&38.2&39.3&19&27.03\\ 
    \system{LaMGD} Tranformer  \hfill{\footnotesize[+0m]} &\SB{23.5}&9.6&\SB{21.5}&32.2&37.7&38.6&40&18.9&27.75 \\
    \hline
  \end{tabular}
  \caption{Multilingual translation}
  \label{tab:multilingual}
\end{table*}

\subsection{Similarity between dropping masks}
\label{ssec:abalation}
This section compares the sub-networks of the domains or the language pairs by computing the average of the similarities between the corresponding dropping masks concatenated through all the layers of the underlying model.

For the multi-domain experiment, we analyze the case of fuzzy domain separation in Section \ref{ssec:fuzzy}. Table \ref{tab:fuzzy-sim} shows that the sub-networks of \domain{law$_1$} and \domain{law$_2$} are identical, which is one of the goals of our method. Furthermore, we remark a large distance between \domain{rel} and the rest of the domains, which correlates to the fact that \domain{rel} has the most distant topic to other domains. \domain{rel} only share around $75 \%$ its active groups with other domains whereas $75 \%$ is the average of sharing proportions by default (see Section \ref{ssec:hyperparams}). In Figure ~\ref{fig:domain}, we visualize the domains using their dropping masks concatenated and mapped to 2D space by PCA.
\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{1cm}|*{7}{r|}} \hline
    & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{bank}}& \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{law$_1$}} & \multicolumn{1}{c|}{\domain{law$_2$}} & \multicolumn{1}{c|}{\domain{rel}} &\multicolumn{1}{c|}{\domain{talk}} \\ \hline 
    \domain{med} &1.0&0.80&0.85&0.83&0.83&0.78&0.89\\
    \domain{bank} &0.80&1.0&0.80&0.90&0.90&0.73&0.82\\
    \domain{it} &0.85&0.80&1.0&0.80&0.80&0.78&0.85\\
    \domain{law$_1$} &0.83&0.90&0.80&1.0&\SB{1.0}&0.75&0.82\\ 
    \domain{law$_2$} &0.83&0.90&0.80&\SB{1.0}&1.0&0.75&0.82\\ 
    \domain{rel} &0.78&0.73&0.78&0.75&0.75&1.0&0.77\\
    \domain{talk} &0.89&0.82&0.85&0.82&0.82&0.77&1.0\\
    \hline
  \end{tabular}
  \caption{Multi-domain sub-networks' similarities}
  \label{tab:fuzzy-sim}
\end{table*}

For multilingual (TED-related) case, the data contain four language families including (1) Turkic family with Azerbaijani and Turkish(\domain{aze},\domain{tur}); (2) Slavic family with Belarusian and Russian (\domain{bel},\domain{rus}); (3) Romance family with Galician and Portuguese (\domain{glg}, \domain{por}); and (4) Czech-Slovak family with Slovak and Czech (\domain{ces}, \domain{slk}). The similarities between the sub-networks for each pair are respectively 0.95, 0.94, 0.99 and 0.96: for each language, the maximally similar one (excluding the diagonoal) is always from the same language family. 
\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{1cm}|*{8}{r|}} \hline
    & \multicolumn{1}{c|}{\domain{aze}} & \multicolumn{1}{c|}{\domain{bel}}& \multicolumn{1}{c|}{\domain{ces}} & \multicolumn{1}{c|}{\domain{glg}} & \multicolumn{1}{c|}{\domain{por}} & \multicolumn{1}{c|}{\domain{rus}} &\multicolumn{1}{c|}{\domain{slk}}&\multicolumn{1}{c|}{\domain{tur}} \\ \hline 
    \domain{aze} &1.0&0.90&0.89&0.86&0.85&0.91&0.89&\SB{0.95}\\
    \domain{bel} &0.90&1.0&0.94&0.91&0.91&\SB{0.94}&0.94&0.88\\
    \domain{ces} &0.89&0.94&1.0&0.92&0.94&0.98&\SB{0.99}&0.91\\
    \domain{glg} &0.86&0.91&0.92&1.0&\SB{0.96}&0.92&0.93&0.86\\ 
    \domain{por} &0.85&0.91&0.94&\SB{0.96}&1.0&0.93&0.94&0.87\\ 
    \domain{rus} &0.91&\SB{0.94}&0.98&0.92&0.93&1.0&0.98&0.93\\
    \domain{slk} &0.89&0.94&\SB{0.99}&0.93&0.94&0.98&1.0&0.91\\
    \domain{tur} &\SB{0.95}&0.88&0.91&0.86&0.87&0.93&0.91&1.0\\
    \hline
  \end{tabular}
  \caption{Multilingual sub-networks' similarities (M2O Ted-related)}
  \label{tab:related-sim}
\end{table*}

We also plot the languages based on their dropout masks in Figure~\ref{fig:visual} using a 2d projection computed by Principal Component Analysis (PCA).
\begin{figure*}[htbp]
\begin{subfigure}{0.5\textwidth}
  \centering
  % include first image
  \includegraphics[width=0.85\textwidth]{ted_related}  
  \caption{TED-Related}
  \label{fig:visual-related}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
  \centering
  % include second image
  \includegraphics[width=0.85\textwidth]{ted_diverse}  
  \caption{TED-Diverse}
  \label{fig:visual-diverse}
\end{subfigure}
\caption{Visualization of languages according to their dropout masks (a large vector concatenating the dropping masks of all the layers of the model) constructed by PCA.}
\label{fig:visual}
\end{figure*}

>>>>

\subsection{System design and configuration}
\subsubsection{Multidomain translation systems}
Our systems for the multidomain experiments are designed as follows:
\begin{itemize}
\item Transformer: The embedding dimension for both encoder and decoder is set as 512, and the feedforward dimension is 2048; the multi-head attention mechanism contains 8 heads;
\item Adapter-based Transformer: The intermediate feedforward dimension is set to 2048;% as in \citet{Pham21revisiting}.
\item \system{LaMGD} Transformer:\fyTodo{Explain acronym} There is no change in the architecture. We group the 512 nodes in each layer into 16 groups of 32 consecutive nodes. For each domain, only 12 out of the 16 groups are selected. The number of parameters of the variational distributions is $k \times L \times n_d$, which is negligible in comparison to the size of the Transformer model.
\end{itemize}

We set the dropout probability to 0.1. We train the multi-domain Transformer model for 20k iterations with a batch size of 12k tokens. We train \system{LaMGD} Tranformer for 300k iterations with a batch size of 12k tokens: these extra iterations are justified by the need for the \system{LaMGD} Tranformer to learn both the sub-networks and the parameters of the underlying Transformer. Finally, we plug domain Adapters to the multidomain Transformer model and finetune them for 25k iterations using the same batch size as the baseline.

@@

We set the dropout probability to 0.3. We train the multilingual Transformer model for 40k iterations with a batch size of 9600 tokens on 16 V100 GPUs as in \citet{Gong21adaptive}. We train \system{LaMGD} Tranformer for 50k iterations with the same batch size. Finally, we finetune the language-specific Adapters for 5k iterations.

@@

For all experiments, we report the BLEU score of \citet{Papineni02bleu} computed with SacreBleu \cite{Post18call}.\fyTodo{Check this}

\subsection{Datasets}
\subsubsection{Multidomain translation}
We use the same data as in the recent work of \citet{Pham21revisiting} on multidomain translation.\fyTodo{Add public to the data link} The datasets for the multidomain translation experiments are detailled in Table~\ref{tab:Corpora-chap4}.
\begin{table*}[h!]
  \centering
  \begin{tabular}{|l|cccccc|} %*{4}{|r|}}
    \cline{2-7} 
    \multicolumn{1}{c|}{} & \multicolumn{1}{c}{\domain{med}} & \multicolumn{1}{c}{\domain{law}} & \multicolumn{1}{c}{\domain{bank}} & \multicolumn{1}{c}{\domain{it}} & \multicolumn{1}{c}{\domain{talk}} & \multicolumn{1}{c}{\domain{rel}} \\
    \hline 
    \# lines & 2609 (0.68) & 501 (0.13) & 190 (0.05) & 270 (0.07) & 160 (0.04) & 130 (0.03) \\
    \# \revisiondone{tokens}  &  133 / 154  &  17.1 / 19.6 &  6.3 / 7.3 &  3.6 / 4.6 &  3.6 / 4.0 &  3.2 / 3.4 \\
    \# \revisiondone{types}  & 771 / 720 & 52.7 / 63.1 & 92.3 / 94.7 & 75.8 / 91.4 & 61.5 / 73.3 & 22.4 / 10.5 \\
    \# \revisiondone{uniq} & 700 / 640 & 20.2 / 23.7 & 42.9 / 40.1 & 44.7 / 55.7 & 20.7 / 25.6 & 7.1 / 2.1 \\
    \hline
  \end{tabular}
  \caption{Corpora statistics: number of parallel lines ($\times 10^3$) and proportion in the basic domain mixture (which does not include the \domain{news} domain), number of tokens in English and French ($\times 10^6$), number of types in English and French ($\times 10^3$), number of types that only appear in a given domain ($\times 10^3$). \domain{med} is the largest domain, containing almost 70\% of the sentences, while \domain{rel} is the smallest, with only 3\% of the data.
  }
\label{tab:Corpora-chap4}
\end{table*}
\subsubsection{Multilingual translation}
We evaluate our model on both one-to-many (O2M) and many-to-one (M2O)
translation tasks borrowing the multilingual translation datasets from past studies. More precisely, we used: 
\begin{itemize}
\item TED8-Related. Following the setting of \citet{Wang20balancing}, we use a subset of translations from \citet{qi18when} between English and eight \emph{related languages}.
\item TED8-Diverse. The dataset consists of parallel sentences between English and eight \emph{diverse languages} as in \citet{Wang20balancing}.
\end{itemize}

@@

\subsection{Multidomain translation}
For these experiments, our main results are in Table ~\ref{tab:mdmt}, where we observe that the \system{LaMGD} Tranformer achieves a significant improvement (+2.78) over the generic \system{Transformer} system with zero extra parameters. Moreover, \system{LaMGD} Tranformer achieves performance that are equivalent on average to that of the \system{Adapter} sytems, which is carrefully finetuned and contains approximately 12.4M additional parameters.
\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{4cm}|*{7}{r|}} \hline
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[65m]} & 40.3 & 59.5 & 49.8 & 36.4 & 49.0 & 80.0  & 52.5\\
    \revision{\system{Adapter}}   \hfill{\footnotesize[+12.4m]}  & 39.5 & 61.0 & 53.1 & 37.5 & 49.6 & 91.0 & 55.3 \\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}  & 40.3 & 60.4 & 52.4 & 39.0 & 52.4 & 87.5 & 55.3 \\ 
    \hline
  \end{tabular}
  \caption{Multi-domain translation}
  \label{tab:mdmt}
\end{table*}

\subsubsection{Fuzzy domain separation}
\label{ssec:fuzzy}
For this experiment, we reuse proposal of \citet{Pham21revisiting}, who measure the efficiency of a multidomain NMT system exploiting the proximity between domains. It uses the same data as in the previous experiment; however, the domain \domain{law} is now randomly split into two pseudo-domains \domain{law$_1$} and \domain{law$_2$} of equal size. A truly multidomain system should be able to automatically detect the proximity between \domain{law$_1$} and \domain{law$_2$}, and there should be no significant difference between the performance of a system trained with the six original domains (including \domain{law}) or with the seven domains (including \domain{law} by \domain{law$_1$} and \domain{law$_2$}). The experiments in \citep{Pham21revisiting} reported a large gap between the two settings when using residual adapters. We replicated this setting and also report the results obtained with the \system{LaMGD} Tranformer system in Table~\ref{tab:fuzzy}.

\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{4cm}|*{3}{r|}} \hline
    Model / Domain & \multicolumn{1}{c|}{\domain{law}} & \multicolumn{1}{c|}{\domain{law$_1$}} & \multicolumn{1}{c|}{\domain{law$_2$}} \\ \hline 
    \system{Adapter}   \hfill{\footnotesize[+25m]}  & 61.0 & 59.4 (-0.6) &  50.2 (-0.8) \\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}  & 61.4 & 61.4 (=) & 61.4 (=) \\ 
    \hline
  \end{tabular}
  \caption{Experiments with two similar pseudo-domains }
  \label{tab:fuzzy}
\end{table*}

The results in Table~\ref{tab:fuzzy} show a performance decrease for the adapter-based system when training with two pseudo-domains \domain{law$_1$} and \domain{law$_2$}. In contrast, the \system{LaMGD} model obtains very stable results. In Section~\ref{ssec:abalation}, we show that our algorithm in fact computes the same sub-network for \domain{law$_1$} and \domain{law$_2$}, that allows a full sharing of information between these two pseudo-domains.

\subsection{Multilingual translation}
Results for the multilingual experiments are in Table~\ref{tab:multilingual}.  The \system{LaMGD} Tranformer achieves an improvement of 0.42, 0.33, 0.32 in average over the multilingual \system{Transformer} in the O2M-related, M2O-related, M2O-diverse conditions, respectively. Significant gains are observed for languages \domain{bel}, \domain{glg} (both direction), \domain{hin} and \domain{bos} (O2M direction) which are very low-resource languages in our sets. However, \system{LaMGD} Tranformer is outperformed by the multilingual \system{Transformer} and Language Adapters for the O2M-diverse condition.
\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{4cm}|*{9}{r|}} \hline
    O2M-related & \multicolumn{1}{c|}{\domain{aze}} & \multicolumn{1}{c|}{\domain{ bel}} & \multicolumn{1}{c|}{\domain{ces}} & \multicolumn{1}{c|}{\domain{glg}} & \multicolumn{1}{c|}{\domain{por}} & \multicolumn{1}{c|}{\domain{rus}} & \multicolumn{1}{c|}{\domain{slk}} & \multicolumn{1}{c|}{\domain{tur}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[91.6m]} & 4.8 &7.3&20.8&21.1&39.7&19.8&22.6&15.2&18.9 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]} &4.3&6.8&21.1&22&39.7&20&23&15.2&19 \\ 
    \system{LaMGD} Tranformer  \hfill{\footnotesize[+0m]}  & 5.2&\SB{9.4}&20.6&\SB{22.8}&39.6&19.6&22.4&15.0&19.33 \\ 
	\hline
    \hline
    M2O-related & \multicolumn{1}{c|}{\domain{aze}} & \multicolumn{1}{c|}{\domain{ bel}} & \multicolumn{1}{c|}{\domain{ces}} & \multicolumn{1}{c|}{\domain{glg}} & \multicolumn{1}{c|}{\domain{por}} & \multicolumn{1}{c|}{\domain{rus}} & \multicolumn{1}{c|}{\domain{slk}} & \multicolumn{1}{c|}{\domain{tur}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[67.8m]} &11.4&16.6&28.5&	27.1&43.7&24.6&30.3&25.6&25.98 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]} &10.1&15.8&28.4&26.8&43.7&24.5&30.2&25.6&25.64\\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}  &11.3&\SB{17.4}&28.6&\SB{28.7}&43.7&24.5&30.7&25.6&26.31 \\ 
    \hline
    \hline
    O2M-diverse & \multicolumn{1}{c|}{\domain{bos}} & \multicolumn{1}{c|}{\domain{mar}} & \multicolumn{1}{c|}{\domain{hin}} & \multicolumn{1}{c|}{\domain{mkd}} & \multicolumn{1}{c|}{\domain{ell}} & \multicolumn{1}{c|}{\domain{bul}} & \multicolumn{1}{c|}{\domain{fra}} & \multicolumn{1}{c|}{\domain{kor}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[96.9m]} & 10.2&4&12.7&22.2&31.8&\SB{34.0}&38.3&8.3&20.19 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]}  &10.2&4&\SB{13.3}&21.9&32.2&\SB{34.1}&38.5&8.3&20.31 \\ 
    \system{LaMGD} Tranformer   \hfill{\footnotesize[+0m]}&10.1&3.8&12.6&\SB{22.8}&31.8&33.4&38.1&8.1&20.09\\
    \hline 
    \hline
    M2O-diverse & \multicolumn{1}{c|}{\domain{bos}} & \multicolumn{1}{c|}{\domain{mar}} & \multicolumn{1}{c|}{\domain{hin}} & \multicolumn{1}{c|}{\domain{mkd}} & \multicolumn{1}{c|}{\domain{ell}} & \multicolumn{1}{c|}{\domain{bul}} & \multicolumn{1}{c|}{\domain{fra}} & \multicolumn{1}{c|}{\domain{kor}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[70.4m]} &22.4&9.7&20.5&31.8&37.5&38.7&39.8&19.0&27.43 \\
    \revision{\system{Adapter}}   \hfill{\footnotesize[13m]}  &22.5&9.4&20.0&30.6&37.2&38.2&39.3&19.0&27.03\\ 
    \system{LaMGD} Tranformer  \hfill{\footnotesize[+0m]} &\SB{23.5}&9.6&\SB{21.5}&32.2&37.7&38.6&40.0&18.9&27.75 \\
    \hline
  \end{tabular}
  \caption{Experiments with multilingual translation.\fyTodo{What is the bold for ?}}
  \label{tab:multilingual}
\end{table*}

\subsection{Similarity between dropping masks}
\label{ssec:abalation}
This section compares the sub-networks learnt for each domain or language pair by computing the average similarity between the corresponding dropout masks concatenated for all the layers of the underlying model. For the multidomain experiment, we analyze the case of pseud-domain separation reported in Section~\ref{ssec:fuzzy} in Table~\ref{tab:fuzzy-sim}. We see that the sub-networks for \domain{law$_1$} and \domain{law$_2$} are identical, yielding a full sharing between the corresponding training sets. Furthermore, we observe a large distance between \domain{rel} and the other domains, which is expected given that \domain{rel} is quite distinct from the other domains. \domain{rel} only share around $75 \%$ its active groups with other domains, as would be obtained by chance in our setting (see Section~\ref{ssec:hyperparams}). In Figure ~\ref{fig:domain}, we visualize the domains using their dropping masks concatenated and mapped to a 2d space using Principal Component Analysis (PCA).

\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{1cm}|*{7}{r|}} \hline
    & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{bank}}& \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{law$_1$}} & \multicolumn{1}{c|}{\domain{law$_2$}} & \multicolumn{1}{c|}{\domain{rel}} &\multicolumn{1}{c|}{\domain{talk}} \\ \hline 
    \domain{med} &1.0&0.80&0.85&0.83&0.83&0.78&0.89\\
    \domain{bank} &0.80&1.0&0.80&0.90&0.90&0.73&0.82\\
    \domain{it} &0.85&0.80&1.0&0.80&0.80&0.78&0.85\\
    \domain{law$_1$} &0.83&0.90&0.80&1.0&\SB{1.0}&0.75&0.82\\ 
    \domain{law$_2$} &0.83&0.90&0.80&\SB{1.0}&1.0&0.75&0.82\\ 
    \domain{rel} &0.78&0.73&0.78&0.75&0.75&1.0&0.77\\
    \domain{talk} &0.89&0.82&0.85&0.82&0.82&0.77&1.0\\
    \hline
  \end{tabular}
  \caption{Multidomain experiments: sub-network similarities}
  \label{tab:fuzzy-sim}
\end{table*}

For multilingual (TED-related) experiments, the training data contains four language families: (1) Turkic, with Azerbaijani and Turkish(\domain{aze},\domain{tur}); (2) Slavic, with Belarusian and Russian (\domain{bel},\domain{rus}); (3) Romance, with Galician and Portuguese (\domain{glg}, \domain{por}); and (4) Czech-Slovak, with Slovak and Czech (\domain{ces}, \domain{slk}). The similarities between the sub-networks for each pair are respectively 0.95, 0.94, 0.99 and 0.96: for each language, the most similar language is always from the same language family. 
\begin{table*}[h!]
  \centering
  \begin{tabular}{|p{1cm}|*{8}{r|}} \hline
    & \multicolumn{1}{c|}{\domain{aze}} & \multicolumn{1}{c|}{\domain{bel}}& \multicolumn{1}{c|}{\domain{ces}} & \multicolumn{1}{c|}{\domain{glg}} & \multicolumn{1}{c|}{\domain{por}} & \multicolumn{1}{c|}{\domain{rus}} &\multicolumn{1}{c|}{\domain{slk}}&\multicolumn{1}{c|}{\domain{tur}} \\ \hline 
    \domain{aze} &1.0&0.90&0.89&0.86&0.85&0.91&0.89&\SB{0.95}\\
    \domain{bel} &0.90&1.0&0.94&0.91&0.91&\SB{0.94}&0.94&0.88\\
    \domain{ces} &0.89&0.94&1.0&0.92&0.94&0.98&\SB{0.99}&0.91\\
    \domain{glg} &0.86&0.91&0.92&1.0&\SB{0.96}&0.92&0.93&0.86\\ 
    \domain{por} &0.85&0.91&0.94&\SB{0.96}&1.0&0.93&0.94&0.87\\ 
    \domain{rus} &0.91&\SB{0.94}&0.98&0.92&0.93&1.0&0.98&0.93\\
    \domain{slk} &0.89&0.94&\SB{0.99}&0.93&0.94&0.98&1.0&0.91\\
    \domain{tur} &\SB{0.95}&0.88&0.91&0.86&0.87&0.93&0.91&1.0\\
    \hline
  \end{tabular}
  \caption{Multilingual sub-networks' similarities (M2O Ted-related)}
  \label{tab:related-sim}
\end{table*}
